---
title: "ABPCameraDesign"
author: "Mathieu Pruvot"
date: "2023-01-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


```{r, include = FALSE}
library(sf)
library(tidyverse)
library(gtsummary)
library(Microsoft365R)
library(janitor)
```

Load and plot data
```{r, include=FALSE}
#?Microsoft365R

#team <- get_team("https://uofc.sharepoint.com/:f:/r/sites/PruvotLab-WildPigProject/")

area <- st_read("C:\\Users\\mpruvot\\OneDrive - University of Calgary\\Wild Pig Project\\Luis\\3. Raw Data\\ABPork camera design\\V4-1_TWP_cameras2.shp")
counties <- st_read("C:\\Users\\mpruvot\\OneDrive - University of Calgary\\Wild Pig Project\\Luis\\3. Raw Data\\ABPork camera design\\RURAL_cameras1.shp")
hotcore <- st_read("C:\\Users\\mpruvot\\OneDrive - University of Calgary\\Wild Pig Project\\Luis\\3. Raw Data\\ABPork camera design\\V4-1_TWP_clip_RURAL_cameras1.shp")
hotcore <- st_make_valid(hotcore)
```


```{r}
plot(st_geometry(counties))
plot(hotcore[1],add=T)




```



```{r, include=FALSE}
ABP <- st_read("C:\\Users\\mpruvot\\Documents\\Work\\UofC\\Research\\Wild pigs\\Data analysis\\Join_ABPtoAGIswine.shp")
AGI <- st_read("C:\\Users\\mpruvot\\Documents\\Work\\UofC\\Research\\Wild pigs\\Data analysis\\AGI_swine.shp")

```



overall farm size distribution
```{r}
ABP %>% 
ggplot(aes(x=HOG))+
  geom_histogram()
```

identify ABP intersecting with county and show size distribution
```{r}
ABP %>% 
st_intersection(counties) %>% 
ggplot(aes(x=HOG))+
  geom_histogram()
```

identify ABP intersecting with core area and show size distribution
```{r}
ABP %>% 
st_intersection(hotcore) %>% 
ggplot(aes(x=HOG))+
  geom_histogram()
```

# Farm selection

Design scheme:
we initially deploy 100 cameras, with the following stratification:

- 15 outdoor and 85 indoor
- among 85: 65 in core area and 20 in broader counties
- among the 65 core cameras: 15 in commercial farms, 50 in backyard farms
- among the 50 : stratify by county, distribute according to size distribution


Outdoor farms: get all 15 outdoor farms in the counties, regardless of size and location

```{r}
Sample_OutdoorFarm <- ABP %>% 
st_intersection(st_union(counties))%>% 
  st_join(y=counties) %>% 
  filter(Pigs_Have=="Yes") 

plot(st_geometry(counties))
plot(hotcore[1],add=T)
plot(st_geometry(Sample_OutdoorFarm),add=T)
```

15 total in the counties

```{r}
Sample_OutdoorFarm %>% 
st_intersection(st_union(hotcore))%>% 
  tabyl(CQA_Status)
```
4 in the core area
this means 11 outside core, including 3 commercials


Select 1 smallholder farm (CQA_Status Not validated) per county that was inside the county but outside core area and the furthest away from the core area, for a total of 20 farms. We excluded Strathcona county, which had extensive coverage by core area (limited additional information to sample county outside of core area)

```{r}
FarmInCounty <- ABP %>% 
st_intersection(st_difference(st_geometry(counties),st_union(hotcore)))%>% 
  st_join(y=counties) %>% 
  filter(Pigs_Have=="No" & !GEONAME%in% c("STRATHCONA COUNTY") & CQA_Status=="Not Validated")

Sample_FarmInCounty <- ABP %>% 
st_intersection(st_difference(st_geometry(counties),st_union(hotcore)))%>% 
  st_join(y=counties) %>% 
  filter(!Pigs_Have=="Yes" & !GEONAME%in% c("STRATHCONA COUNTY") & CQA_Status=="Not Validated") %>% 
  mutate(distcore=st_distance(x=.,y=st_union(hotcore))) %>% 
  group_by(GEONAME) %>% 
  arrange(desc(distcore)) %>% 
  slice(1) %>% 
  select(-distcore)
```

Control that the most remote was selected by comparing selected map and map of smallholder in county outside core
```{r}
plot(st_geometry(counties))
plot(hotcore[1],add=T)
plot(st_geometry(Sample_FarmInCounty),add=T)

plot(st_geometry(counties))
plot(hotcore[1],add=T)
plot(st_geometry(FarmInCounty),add=T)
```

among the 65 core cameras: 15 in commercial farms


Not enough commercial farms in core area, so used a 10k buffer around core
```{r}
CommFarmInCore <- ABP %>% 
st_intersection(st_buffer(st_union(hotcore),dist=10000))%>% 
  st_join(y=counties) %>% 
  filter(!Pigs_Have=="Yes" & CQA_Status %in% c("Valid"))


Sample_CommFarmInCore <- CommFarmInCore %>% 
  group_by(GEONAME) %>% 
  sample_n(size=1)
```
This resulted in 12 commercial farms

Here is the map
```{r}
plot(st_geometry(counties))
plot(hotcore[1],add=T)
plot(st_geometry(Sample_CommFarmInCore),add=T)


```

Look at number of large farms per county and identify the 4 counties with the most large farms


```{r}
ManyCommFarm <- CommFarmInCore %>% 
  group_by(GEONAME) %>% 
  summarize(n=n()) %>% 
  arrange(desc(n)) %>% 
  filter(!is.na(GEONAME)) %>% 
  slice(1:4) %>% 
  select(GEONAME) %>% 
  as.data.frame() %>% 
  select(GEONAME)

ManyCommFarm
```

Select an additional 4 farms from counties that have the most farms and add to the previous selection
```{r}
Sample_CommFarmInCore <- CommFarmInCore %>% 
  filter(GEONAME %in% ManyCommFarm$GEONAME & !Premises_I %in% Sample_CommFarmInCore$Premises_I) %>% 
  group_by(GEONAME) %>% 
  sample_n(size=1) %>% 
  rbind(Sample_CommFarmInCore)
```

among the 50 smallholder in core: stratify by county, distribute according to size distribution

Select all indoor smallholder farms in the core
```{r}
SmallFarmInCore <- ABP %>% 
st_intersection(st_union(hotcore))%>% 
  st_join(y=counties) %>% 
  filter(!Pigs_Have=="Yes" & CQA_Status=="Not Validated")


plot(st_geometry(counties))
plot(hotcore[1],add=T)
plot(st_geometry(SmallFarmInCore),add=T)
```

inspect size distribution. Take farms with HOG>2, because more relevant to pathogen transmission if not just isolated animals. Happens to provide 52 farms
```{r}
SmallFarmInCore %>% 
  filter(HOG>2) %>% 
  select(HOG) %>% 
  summary()
```


```{r}

Sample_SmallFarmInCore <- SmallFarmInCore %>% 
  filter(HOG>2)


```

```{r}
plot(st_geometry(counties))
plot(hotcore[1],add=T)
plot(st_geometry(Sample_SmallFarmInCore),add=T)

```
```{r}
Sample_Total <- rbind(Sample_CommFarmInCore,Sample_FarmInCounty, Sample_OutdoorFarm, Sample_SmallFarmInCore)
#save(Sample_Total,file="Sample_Total.Rdata")
```

```{r}
plot(st_geometry(counties))
plot(hotcore[1],add=T)
plot(st_geometry(Sample_Total),add=T)
```


